\papertitle

### 2014-03-18 final-report/paper.tex
Short paragraph about overview chart

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graph}{Physical Query Plan\xspace}
\newcommand*{\fragment}{Fragment Execution\xspace}
\newcommand*{\network}{Worker Communication\xspace}
\newcommand*{\overall}{Fragment Overall\xspace}

@@

% What is myria, how does it work (look at report from last quarter but shorter), which query languages are supported
% motivation
% questions (inspiration: https://docs.google.com/a/uw.edu/document/d/1Syn65bu_p6S4RQETaozsleYcRBauQJ7IduYrctS1wrw/edit?pli=1#)
% why is a visualization a good way to answer the questions
% so far the only performance debug mechanism is runtime
% contributions

@@

\subsubsection{Fragment execution view}

@@

The \fragment view comprises two charts: the utilization chart and the
operators chart. The utilization chart (Fig.~\ref{fig:utilization_chart}) shows the utilization
of the cluster over time, inside the selected fragment. The chart is used to
quickly reveal any patterns in the schedule, like tail latency, long periods of
idleness, etc. We implemented a small brush (at the top of the figure) that
allows the user to zoom-in and further analyze the problematic area.

@@

>>>>

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graph}{Physical Query Plan\xspace}
\newcommand*{\fragment}{Fragment Execution\xspace}
\newcommand*{\overview}{Fragment Overview\xspace}
\newcommand*{\network}{Worker Communication\xspace}
\newcommand*{\overall}{Fragment Overall\xspace}

@@

% What is myria, how does it work (look at report from last quarter but shorter), which query languages are supported
% motivation
% questions (inspiration: https://docs.google.com/a/uw.edu/document/d/1Syn65bu_p6S4RQETaozsleYcRBauQJ7IduYrctS1wrw/edit?pli=1#)
% why is a visualization a good way to answer the questions
% so far the only performance debug mechanism is runtime
% contributions
% explain difference between execution and data skew

@@

\subsubsection{Fragment execution view}
\label{sec:fragment}

@@

The \fragment view comprises two charts: the utilization chart and the
operators chart. The utilization chart (Fig.~\ref{fig:utilization_chart}) shows on
how many workers a fragment is running over time. The chart is used to
quickly reveal any patterns in the schedule, like tail latency, long periods of
idleness, etc. We implemented a small brush (at the top of the figure) that
allows the user to zoom-in and further analyze the problematic area.

@@

% Dom

The \overview shows small multiples of the utilization chart as described in the previous section.
Execution skew can be spotted in this view. Furthermore, the user can compare the fragments and find
correlations between the execution of different fragments. This view helps the user navigate to the
right fragment and is not intended to offer further inside into the causes or performance problems.
